Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-04 mr-review.Rmd
abbreviated MR

Three assumptions are central to Mendelian Randomization. Satisfying them is necessary to infer 
causal effects in an observational MR study. Careful evaluation of the assumptions is needed. Briefly, 
the first assumption states that the exposure is associated with the outcome. The second requires 
independence, conditional on the exposure and all measured and unmeasured confounders, between the 
genetic marker and the outcome. The last of the three assumptions states that the genetic marker is 
independent of all (measured and unmeasured) confounders of the relationship between exposure and 
outcome. We next discuss these in more detail and consider their evaluation in MR studies.

@@

Recognition of complex traits' diverse genetic architectures has fueled development of MR methods with multiple instruments [@Boyle2017].

>>>>

Three assumptions are central to MR. Satisfying them is necessary to infer 
causal effects in an observational MR study. Careful evaluation of the assumptions is needed. Briefly, 
the first assumption states that the exposure is associated with the outcome. The second requires 
independence, conditional on the exposure and all measured and unmeasured confounders, between the 
genetic marker and the outcome. The last of the three assumptions states that the genetic marker is 
independent of all (measured and unmeasured) confounders of the relationship between exposure and 
outcome. We next discuss these in more detail and consider their evaluation in MR studies.

@@

Recognition of complex traits' diverse genetic architectures has fueled development of two-sample MR methods with multiple instruments [@Boyle2017].
